\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-06 paper.qmd
Added mathemtical expression for triangulation

@@

>>>>

The mathematical expression for the hexagonal bin centers can be defined based on the hexagonal grid coordinates. Let's denote the hexagonal grid coordinates as \( (q, r) \), where \( q \) and \( r \) are integers representing the coordinates of the hexagon in the grid.

For a regular hexagonal grid, the coordinates of the hexagon centers can be calculated using the following formulas:
<!--
\[
x = \frac{3}{2} \times q \times s
\]
\[
y = \frac{\sqrt{3}}{2} \times q \times s + \sqrt{3} \times r \times s
\]-->

Where:
- \( s \) is the side length of the hexagon.
- \( q \) represents the column index of the hexagon in the grid.
- \( r \) represents the row index of the hexagon in the grid.
- \( x \) and \( y \) are the Cartesian coordinates of the center of the hexagon.

This formula calculates the \( x \) and \( y \) coordinates of the center of each hexagon based on its grid coordinates \( q \) and \( r \), allowing you to determine the position of each hexagon in the plane.

@@

Delaunay triangulation is a geometric algorithm used to create a triangular mesh from a set of points in a plane. The key principle behind Delaunay triangulation is to connect points in such a way that no point falls within the circumcircle of any triangle formed by the points.

Mathematically, given a set of points \( P \) in a plane, the Delaunay triangulation constructs a set of triangles such that:

1. Each triangle is formed by connecting three points from \( P \).
2. No point in \( P \) is inside the circumcircle of any triangle in the triangulation.

Formally, the Delaunay triangulation can be defined as follows:

Let \( P = \{p_1, p_2, ..., p_n\} \) be a set of \( n \) points in the plane. The Delaunay triangulation of \( P \), denoted as \( DT(P) \), is a triangulation of the convex hull of \( P \) such that the circumcircle of every triangle in the triangulation contains no other points from \( P \).

### 2024-03-06 paper.tex
Added mathemtical expression for triangulation

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, frame hidden, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

@@

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The mathematical expression for the hexagonal bin centers can be defined
based on the hexagonal grid coordinates. Let's denote the hexagonal grid
coordinates as ( (q, r) ), where ( q ) and ( r ) are integers
representing the coordinates of the hexagon in the grid.

For a regular hexagonal grid, the coordinates of the hexagon centers can
be calculated using the following formulas:

Where: - ( s ) is the side length of the hexagon. - ( q ) represents the
column index of the hexagon in the grid. - ( r ) represents the row
index of the hexagon in the grid. - ( x ) and ( y ) are the Cartesian
coordinates of the center of the hexagon.

This formula calculates the ( x ) and ( y ) coordinates of the center of
each hexagon based on its grid coordinates ( q ) and ( r ), allowing you
to determine the position of each hexagon in the plane.

@@

Delaunay triangulation is a geometric algorithm used to create a
triangular mesh from a set of points in a plane. The key principle
behind Delaunay triangulation is to connect points in such a way that no
point falls within the circumcircle of any triangle formed by the
points.

Mathematically, given a set of points ( P ) in a plane, the Delaunay
triangulation constructs a set of triangles such that:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Each triangle is formed by connecting three points from ( P ).
\item
  No point in ( P ) is inside the circumcircle of any triangle in the
  triangulation.
\end{enumerate}

Formally, the Delaunay triangulation can be defined as follows:

Let ( P = \{p\_1, p\_2, \ldots, p\_n\} ) be a set of ( n ) points in the
plane. The Delaunay triangulation of ( P ), denoted as ( DT(P) ), is a
triangulation of the convex hull of ( P ) such that the circumcircle of
every triangle in the triangulation contains no other points from ( P ).
